Mock community evaluation

### 2022-03-24 06--mock_community.Rmd
imporved read proporion plot for reviewer

```{r message=FALSE}
library(dplyr)
library(purrr)
library(furrr)
library(tidyr)
library(readr)
library(ggplot2)
library(sessioninfo)
library(metacoder)
library(vegan)
library(viridis)
library(taxize)
library(purrr)
library(ape)
library(ips)
library(insect)
library(phangorn)
library(DT)
library(gridExtra)
library(stringr)
library(Biostrings)
```

@@

```{r}
rps10_best_mc_hits$abund <- rps10_best_mc_hits$abund / sum(rps10_best_mc_hits$abund)
its_best_mc_hits$abund <- its_best_mc_hits$abund / sum(its_best_mc_hits$abund)
plot_data <- rbind(mutate(rps10_best_mc_hits, locus = "Rps10"), mutate(its_best_mc_hits, locus = "ITS1"))
mc_read_prop_plot <- plot_data %>%
  ggplot(aes(x = locus, y = abund)) +
  geom_boxplot() +
  geom_hline(yintercept=1/24, linetype="dashed") +
  labs(x = "Locus", y = "Read Proportion")
mc_read_prop_plot
ggsave(mc_read_prop_plot, filename = 'read_proportion_of_mock_community.pdf', path = file.path('results'), width = 5, height = 5)
```

@@

```{r}
plot_data %>%
  pivot_wider(names_from = locus, values_from = abund) %>%
  ggplot(aes(x = Rps10, y = ITS1)) +
  geom_point()
```

>>>>

```{r message=FALSE}
library(dplyr)
library(purrr)
library(furrr)
library(tidyr)
library(readr)
library(ggplot2)
library(sessioninfo)
library(metacoder)
library(vegan)
library(viridis)
library(taxize)
library(purrr)
library(ape)
library(ips)
library(insect)
library(phangorn)
library(DT)
library(gridExtra)
library(stringr)
library(Biostrings)
library(ggpubr)
```

@@

```{r}
rps10_best_mc_hits$abund <- rps10_best_mc_hits$abund / sum(rps10_best_mc_hits$abund)
its_best_mc_hits$abund <- its_best_mc_hits$abund / sum(its_best_mc_hits$abund)
plot_data <- rbind(mutate(rps10_best_mc_hits, locus = "Rps10"), mutate(its_best_mc_hits, locus = "ITS1"))
mc_read_prop_plot <- plot_data %>%
  ggplot(aes(x = locus, y = abund)) +
  geom_boxplot() +
  geom_hline(yintercept=1/24, linetype="dashed") +
  labs(x = "Locus", y = "Read Proportion") +
  theme_minimal() 
mc_read_prop_plot
```

@@

```{r}
plot_data$obligate <- plot_data$species %in% c("Peronospora effusa", "Peronospora schachtii", "Plasmopara halstedii", "Plasmopara obducens", "Pseudoperonospora cubensis")
plot_data$low_dna <- plot_data$species %in% c("Phytophthora pluvialis", "Saprolegnia diclina")
plot_data$dna_type <- "Normal"
plot_data$dna_type[plot_data$obligate] <- "Obligate"
plot_data$dna_type[plot_data$low_dna] <- "Less DNA"
plot_data$species[plot_data$species == "Pythium citrinum"] <- "Phytopythium citrinum"
read_prop_corr_plot <- plot_data %>%
  select(species, abund, locus, obligate, low_dna, olbigate_or_low_dna, dna_type) %>%
  pivot_wider(names_from = locus, values_from = abund) %>%
  ggplot(aes(x = Rps10, y = ITS1, color = dna_type)) +
  geom_point(alpha= 0.5) +
  coord_fixed(xlim = c(0, 0.3), ylim = c(0, 0.3)) +
  labs(x = "Rps10 read proportion", y = "ITS1 read proportion", color = "DNA type") +
  theme_minimal() 
read_prop_corr_plot
```

Lets combine these two plots since they both describe the same data

```{r}
mc_plot_combined <- ggarrange(mc_read_prop_plot, read_prop_corr_plot,
                              labels = c("A", "B"),
                              widths = c(.55, 1),
                              ncol = 2, nrow = 1)
mc_plot_combined
ggsave(mc_plot_combined, filename = 'read_proportion_of_mock_community.pdf', path = file.path('results'), width = 10, height = 5)
```
